Fast Regression of the Tritium Breeding Ratio in Fusion Reactors

### 2020-06-18 paper/acknowledgements.tex
reference online resources
re-enable STFC acknowledgement, add EUROfusion acknowledgement

PM was supported the STFC UCL Centre for Doctoral Training in Data Intensive
Science (grant no. ST/P006736/1).

>>>>

{\footnotesize
PM \& GVG were supported the STFC UCL Centre for Doctoral Training in Data Intensive
Science (grant no. ST/P006736/1).
This work has been carried out within the framework of the EUROfusion consortium and has received funding from the Euratom research and training programme 2014-2018 and 2019-2020 under grant agreement No 633053. The views and opinions expressed herein do not necessarily reflect those of the European Commission.
}
